\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-01 coq-example.tex
Update statistic infomation about Parser example.
stuff

\subsection{Type Safety for STLC}\EDJ{We need a fuller view of the two examples. Especially show "accessing family components outside that family".}

@@

\subsection{Abstract Interpreters for \texttt{Imp}}\YZ{Try to have two runnable interpreter -- choose another simple one like constant propagation. and remove LangMore}
The second example is adapted and modified from \citet{zm2017}.
Contrary to our first example, here, we use a big-step interpreter with fuel
as the operational semantics of an imperative language with
side effects, and we specify the abstract interpretation and prove its
soundness, with some postulation on both computation and property. Then we instantiate our abstract interpretation with two concrete computation---one for type inference and the other for constant propagation. Our analyzer will return the analysis result about the end of the program, e.g. our constant propagator will return what constant value each variable is at the end of the program. Thanks to the compilation to Coq module, we can directly run the resulting
abstract interpreters.

@@

\subsection{An Extensible Decision Procedure for Parsing}
The third example is a decision procedure for parsing, based on the fact that, we can use Cop's Inductive Facility to encode CFG rules. Thus extensible inductive family corresponds to extensible CFG rules. For example, indexed type \mintinline{Coq}{is_prog : strs → Type} is a predicate asserting if a token list is a syntactically well-formed program.

@@

We will have challenges maintaining this equivalence proof. From left to right (soundness), we can have incremental construction and proof reuse throughout different families---we can easily prove "is_prog l" using each constructor. However, from right to left (completeness), the proof from the parent family cannot be reused in the children as "alg_is_prog" is changing and the proposition itself is changing.

>>>>

\subsection{Type Safety for STLC}\EDJ{We need a fuller view of the two examples. Especially show "accessing family components outside that family".}
\label{sec:coqexample-stlc}

@@

\subsection{Abstract Interpreters for \texttt{Imp}}\YZ{Try to have two runnable interpreter -- choose another simple one like constant propagation. and remove LangMore}
\label{sec:coqexample-analysis}
The second example is adapted and modified from \citet{zm2017}.
Contrary to our first example, here, we use a big-step interpreter with fuel
as the operational semantics of an imperative language with
side effects, and we specify the abstract interpretation and prove its
soundness, with some postulation on both computation and property. Then we instantiate our abstract interpretation with two concrete computation---one for type inference and the other for constant propagation. Our analyzer will return the analysis result about the end of the program, e.g. our constant propagator will return what constant value each variable is at the end of the program. Thanks to the compilation to Coq module, we can directly run the resulting
abstract interpreters.

@@

\subsection{An Extensible Decision Procedure for Parsing}
\label{sec:coqexample-parser}
The third example is a decision procedure for parsing, based on the fact that, we can use Cop's Inductive Facility to encode CFG rules. Thus extensible inductive family corresponds to extensible CFG rules. For example, indexed type \mintinline{Coq}{is_prog : strs → Type} is a predicate asserting if a token list is a syntactically well-formed program.

@@

We will have challenges maintaining this equivalence proof. From left to right (soundness), we can have incremental construction and proof reuse throughout different families---we can easily prove "is_prog l" using each constructor. However, from right to left (completeness), the proof from the parent family cannot be reused in the children as "alg_is_prog" is changing and the proposition itself is changing. So we use "overridable" to organize the proof of completeness.

It is around 750 lines of codes using Family facility and around 900 lines of code using vanilla Coq. Around 350 lines of them are public helper function used by both implementations.

### 2022-11-01 coqimpl.tex
stuff

\begin{itemize}
\item Parameterized by enclosing family "self": explicit extensibility hooks
\item "self" includes only those fields in the context
\item Extensible inductive type $\Rightarrow$ axiomatize
\item Further-bindable \lsti{FRecursion} $\Rightarrow$ axiomatize
\item Non-overridable definitions $\Rightarrow$ expose definitional equality
\item Instantiate inductive types, partial recursors, and equalities $\Rightarrow$ OK to use recursor; equalities easily discharged by \lsti{reflexivity}
\item Instantiate recursion/induction and equalities $\Rightarrow$ OK to use recursor; equalities easily discharged by \lsti{reflexivity}\\
      Code reuse
\end{itemize}

>>>>

\begin{itemize}
\item Parameterized by enclosing family "self": explicit extensibility hooks
\item "self" includes only those fields in the context
\item Extensible inductive type $\Rightarrow$ axiomatize
\item Further-bindable \lsti{FRecursion} $\Rightarrow$ axiomatize
\item Non-overridable definitions $\Rightarrow$ expose definitional equality
\item Instantiate inductive types, partial recursors, and equalities $\Rightarrow$ OK to use recursor; equalities easily discharged by \lsti{reflexivity}
\item Instantiate definition of recursive functions (induction proofs) and equalities $\Rightarrow$ OK to use recursor; equalities easily discharged by \lsti{reflexivity}\\
      Code shared by code compiled for derived families
\item Include 
\end{itemize}

\ifShowOldWriting

### 2022-11-01 metatheory-condensed.tex
stuff

\input{selected-typing.tex}

@@

\cref{fig:typing-selected} presents the syntax and selected typing rules of \TT.
The new forms (relative to MLTT) are highlighted.
We briefly review the base MLTT fragment first.

As is standard in MLTT presentations, we use explicit substitutions~\cite{substcalculus,abadi1989subst}:
substitutions~$\gm$ and their applications (e.g., \sub{T}{\gm}) are part
of the syntax rather than meta-operations.
%
Variables are represented by de Bruijn indices:
\var{n} is the variable bound by the $n$-th closest enclosing binder.
For example, $\lambda x.\,\lambda y.\,x$ is $\lam{\lam{\var{1}}}$.
%
Typing judgments for substitutions have the form 
%\EDJ{It seems to me G |- g : D is a judgement not a rule. Rules usually have two parts (premises + conclusion). Judgment is a standard terminology invented by Martin Lof (https://ncatlab.org/nlab/show/judgment see reference here). I will suggest saying 'Formation rules for substitution lead to a judgement G |- g : D' sth like this. In pen-and-paper, the formation rule (corresponding to QIIT well-typed-ness of judgement) is called presuppose (can be found in Modal MLTT paper) }
$\goodSub{\Gm}{\gm}{\Dl}$.
The idea is that applying~$\gm$ to terms valid in the context~$\Dl$
yields terms valid in~$\Gm$ (e.g., rule \ruleref{tm/sub}).
%
The two main forms of substitutions are weakening (\ruleref{sub/wk}) and extension (\ruleref{sub/ext}):
\sub{t}{\SubstWeak{n}} introduces $n$ free variables into the context of $t$, and
\sub{t}{\SubstExt{\gm}{t'}} substitutes~$t'$ for~$\var{0}$ in~$t$ and
then applies~$\gm$.
For example, rule \ruleref{tm/proj} states that if $t$ is a dependent pair
that has type $\TySigma{A}{B}$, then $\snd{t}$ has type
$\sub{B}{\SubstExt{\SubstWeak{0}}{\fst{t}}}$.

>>>>

\input{mltt-selected.tex}
\input{fmltt-selected.tex}

@@

\cref{fig:mltt-selected} presents the syntax and selected typing rules of MLTT, and
\cref{fig:fmltt-selected} \TT.
%The new forms (relative to MLTT) are highlighted.
We briefly review the base MLTT fragment first.

As is standard in MLTT presentations, we use explicit substitutions~\cite{substcalculus,abadi1989subst}:
substitutions~$\gm$ and their applications (e.g., \sub{T}{\gm}) are part
of the syntax rather than meta-operations.
%
Variables are represented by de Bruijn indices:
\var{n} is the variable bound by the $n$-th closest enclosing binder.
For example, $\lambda x.\,\lambda y.\,x$ is $\lam{\lam{\var{1}}}$.
%
Typing judgments for substitutions have the form 
%\EDJ{It seems to me G |- g : D is a judgement not a rule. Rules usually have two parts (premises + conclusion). Judgment is a standard terminology invented by Martin Lof (https://ncatlab.org/nlab/show/judgment see reference here). I will suggest saying 'Formation rules for substitution lead to a judgement G |- g : D' sth like this. In pen-and-paper, the formation rule (corresponding to QIIT well-typed-ness of judgement) is called presuppose (can be found in Modal MLTT paper) }
$\goodSub{\Gm}{\gm}{\Dl}$.
The idea is that applying~$\gm$ to terms valid in the context~$\Dl$
yields terms valid in~$\Gm$ (e.g., rule \ruleref{tm/sub}).
%
The two main forms of substitutions are weakening (\ruleref{sub/wk}) and extension (\ruleref{sub/ext}):
\sub{t}{\SubstWeak{n}} introduces $n$ free variables into the context of $t$, and
\sub{t}{\SubstExt{\gm}{t'}} substitutes~$t'$ for~$\var{0}$ in~$t$ and
then applies~$\gm$.
For example, rule \ruleref{tm/snd} states that if $t$ is a dependent pair
that has type $\TySigma{A}{B}$, then $\snd{t}$ has type
$\sub{B}{\SubstExt{\SubstWeak{0}}{\fst{t}}}$.

### 2022-11-01 stlc-compiled.tex
stuff

[@\outdent@][@\dadada@][@\hfill\codecomment{Code emitted upon definition of \texttt{ty} in family \texttt{STLC}}@][@\tanc{c-STLC-ty-start}@][@\tanc{c-STLC-ty-end}@][@\outersep@]

@@

[@\outdent@][@\dadada@][@\hfill\codecomment{Code emitted for other fields defined in family \texttt{STLC}}@][@\tanc{c-STLC-rest}@][@\outersep@]

@@

\makeline[-1pt]{c-STLC-subst-start}{c-STLC-subst-end}[codecomment-color!55][1.8pt]
\makeline[-1pt]{c-STLC-tm-start}{c-STLC-tm-end}[codecomment-color!55][1.8pt]
\makeline[-1pt]{c-STLC-ty-start}{c-STLC-ty-end}[codecomment-color!55][1.8pt]
\makeline[-1pt]{c-STLC-env-start}{c-STLC-env-end}[codecomment-color!55][1.8pt]
\makeline[-1pt]{c-STLC-rest}{c-STLC-rest}[codecomment-color!55][1.8pt]
\makeline[-1pt]{c-STLC-start}{c-STLC-firstcol-end}[codecomment-color!55][1.8pt]
\makeline[4pt]{c-STLC-d-tm-start}{c-STLC-d-tm-end}[codecomment-color!35][1.0pt]
\makeline[4pt]{c-STLC-d-subst-start}{c-STLC-firstcol-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+8pt]{c-STLC-sndcol-start}{c-STLC-end}[codecomment-color!55][1.8pt]
\makeline[.5\textwidth+12pt]{c-STLC-d-ty}{c-STLC-d-ty}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLC-d-env}{c-STLC-d-env}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLC-d-rest}{c-STLC-d-rest}[codecomment-color!35][1.0pt]

@@

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{tm} in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-tm-start}@]
[@\outdent@]Module Type STLCFix\_tm\_Ctx.
[@\outdent@]End STLCFix\_tm\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_tm (self : STLCFix\_tm\_Ctx).
Include STLC\_tm(self).
Axiom tm_fix : id -> tm -> tm.
Axiom tm_fix_eq_STLC : \forall[@\,@][@\dadada@],[@\,@]tm_prect_STLC [@\dadada@][@\;@]=[@\;@]None.
Axiom tm_prect_STLCFix : [@\dadada@].
Axiom tm_fix_eq_STLCFix : [@\dadada@].
[@\outdent@]End STLCFix\_tm.[@\tanc{c-STLCFix-tm-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-subst-start}@]
[@\outdent@]Module Type STLCFix\_subst\_Ctx.
Include STLCFix\_tm\_Ctx. Include STLCFix\_tm.
[@\outdent@]End STLCFix\_subst\_Ctx.[@\innersep@]
[@\outdent@]Module STLCFix\_subst\_Cases (self[@\,@]:[@\,@]STLCFix\_subst\_Ctx).
Include STLC\_subst\_Cases(self).
Def subst\_tm_fix := [@\dadada@].
[@\outdent@]End STLCFix\_subst\_Cases.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst (self[@\,@]:[@\,@]STLCFix\_subst\_Ctx).
Include STLC\_subst(self).
Axiom subst_tm_fix_eq : [@\dadada@].
[@\outdent@]End STLCFix\_subst.[@\tanc{c-STLCFix-subst-end}@][@\outersep@]
[@\outdent@][@\dadada@] [@\codecomment{Code emitted for other fields defined in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-rest}@][@\outersep@]
[@\outdent\codecomment{Code emitted upon completion of family \texttt{STLCFix}}@][@\tanc{c-STLCFix-start}@]
[@\outdent@]Module STLCFix.[@\innersep@]
Inductive tm\_ : Set :=[@\tanc{c-STLCFix-d-tm-start}@]
| tm_unit\_[@\,@]:[@\,@]tm\_ | tm_var\_[@\,@]:[@\,@]id -> tm\_
| tm_abs\_[@\,@]:[@\,@]id->tm\_->tm\_ | tm_app\_[@\,@]:[@\,@]tm\_->tm\_->tm\_
| tm_fix\_[@\,@]:[@\,@]id->tm\_->tm\_.
Def tm := tm\_.[@\hfill\codecomment{Instantiate \texttt{tm} \& its constructors}@]
Def tm_unit := tm_unit\_. Def tm_var := tm_var\_.
Def tm_abs  := tm_abs\_.  Def tm_app := tm_app\_.
Def tm_fix  := tm_fix\_.
[@\dadada@][@\hfill\codecomment{Instantiate \texttt{tm} partial recursors \& their equalities}@][@\tanc{c-STLCFix-d-tm-end}@][@\innersep@]
Include STLCFix\_subst\_Cases. [@\tanc{c-STLCFix-d-subst-start}@]
Def subst :=[@\hfill\codecomment{Instantiate \texttt{subst} \& its equalities}@]
  tm\__rect _ subst\_tm_unit subst\_tm_var
             subst\_tm_abs  subst\_tm_app subst\_tm_fix.
Fact[@\;@][@\textls[-40]{subst\_tm\_unit\_eq}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLCFix-d-subst-end}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{\textls[-10]{Instantiate \texttt{ty}, its constructors, partial recursor \& eq.}}@][@\tanc{c-STLCFix-d-ty}@][@\innersep@]
Include STLC\_env.[@\hfill\codecomment{Include \texttt{env}}@][@\tanc{c-STLCFix-d-env}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{Include/Instantiate other fields of family \texttt{STLCFix}}@][@\tanc{c-STLCFix-d-rest}@][@\innersep@]
[@\outdent@]End STLCFix.[@\tanc{c-STLCFix-end}@]
\end{lstlisting}

\makeline[.5\textwidth+8pt]{c-STLCFix-tm-start}{c-STLCFix-tm-end}[codecomment-color!55][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-subst-start}{c-STLCFix-subst-end}[codecomment-color!55][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-rest}{c-STLCFix-rest}[codecomment-color!55][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-start}{c-STLCFix-end}[codecomment-color!55][1.8pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-tm-start}{c-STLCFix-d-tm-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-subst-start}{c-STLCFix-d-subst-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-ty}{c-STLCFix-d-ty}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-env}{c-STLCFix-d-env}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-rest}{c-STLCFix-d-rest}[codecomment-color!35][1.0pt]

>>>>

[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{ty} in family \texttt{STLC}}@] [@\dadada@][@\tanc{c-STLC-ty-start}@][@\tanc{c-STLC-ty-end}@][@\outersep@]

@@

[@\outdent@][@\codecomment{Code emitted for other fields defined in family \texttt{STLC}}@] [@\dadada@][@\tanc{c-STLC-rest}@][@\outersep@]

@@

\makeline[-1pt]{c-STLC-subst-start}{c-STLC-subst-end}[codecomment-color!50][1.8pt]
\makeline[-1pt]{c-STLC-tm-start}{c-STLC-tm-end}[codecomment-color!50][1.8pt]
\makeline[-1pt]{c-STLC-ty-start}{c-STLC-ty-end}[codecomment-color!50][1.8pt]
\makeline[-1pt]{c-STLC-env-start}{c-STLC-env-end}[codecomment-color!50][1.8pt]
\makeline[-1pt]{c-STLC-rest}{c-STLC-rest}[codecomment-color!50][1.8pt]
\makeline[-1pt]{c-STLC-start}{c-STLC-firstcol-end}[codecomment-color!50][1.8pt]
\makeline[4pt]{c-STLC-d-tm-start}{c-STLC-d-tm-end}[codecomment-color!35][1.0pt]
\makeline[4pt]{c-STLC-d-subst-start}{c-STLC-firstcol-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+8pt]{c-STLC-sndcol-start}{c-STLC-end}[codecomment-color!50][1.8pt]
\makeline[.5\textwidth+12pt]{c-STLC-d-ty}{c-STLC-d-ty}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLC-d-env}{c-STLC-d-env}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLC-d-rest}{c-STLC-d-rest}[codecomment-color!35][1.0pt]

@@

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{tm} in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-tm-start}@]
[@\outdent@]Module Type STLCFix\_tm\_Ctx.
[@\outdent@]End STLCFix\_tm\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_tm (self : STLCFix\_tm\_Ctx).
Include STLC\_tm(self).
Axiom tm_fix : id -> tm -> tm.
Axiom tm_fix_eq_STLC : \forall[@\,@][@\dadada@],[@\,@]tm_prect_STLC [@\dadada@][@\;@]=[@\;@]None.
Axiom tm_prect_STLCFix : [@\dadada@].
Axiom tm_fix_eq_STLCFix : [@\dadada@].
[@\outdent@]End STLCFix\_tm.[@\tanc{c-STLCFix-tm-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-subst-start}@]
[@\outdent@]Module Type STLCFix\_subst\_Ctx.
Include STLCFix\_tm\_Ctx. Include STLCFix\_tm.
[@\outdent@]End STLCFix\_subst\_Ctx.[@\innersep@]
[@\outdent@]Module STLCFix\_subst\_Cases (self[@\,@]:[@\,@]STLCFix\_subst\_Ctx).
Include STLC\_subst\_Cases(self).
Def subst\_tm_fix := [@\dadada@].
[@\outdent@]End STLCFix\_subst\_Cases.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst (self[@\,@]:[@\,@]STLCFix\_subst\_Ctx).
Include STLC\_subst(self).
Axiom subst_tm_fix_eq : [@\dadada@].
[@\outdent@]End STLCFix\_subst.[@\tanc{c-STLCFix-subst-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted for other fields defined in family \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-rest}@][@\outersep@]
[@\outdent\codecomment{Code emitted upon completion of family \texttt{STLCFix}}@][@\tanc{c-STLCFix-start}@]
[@\outdent@]Module STLCFix.[@\innersep@]
Inductive tm\_ : Set :=[@\tanc{c-STLCFix-d-tm-start}@]
| tm_unit\_[@\,@]:[@\,@]tm\_ | tm_var\_[@\,@]:[@\,@]id -> tm\_
| tm_abs\_[@\,@]:[@\,@]id->tm\_->tm\_ | tm_app\_[@\,@]:[@\,@]tm\_->tm\_->tm\_
| tm_fix\_[@\,@]:[@\,@]id->tm\_->tm\_.
Def tm := tm\_.[@\hfill\codecomment{Instantiate \texttt{tm} \& its constructors}@]
Def tm_unit := tm_unit\_. Def tm_var := tm_var\_.
Def tm_abs  := tm_abs\_.  Def tm_app := tm_app\_.
Def tm_fix  := tm_fix\_.
[@\dadada@][@\hfill\codecomment{Instantiate \texttt{tm} partial recursors \& their equalities}@][@\tanc{c-STLCFix-d-tm-end}@][@\innersep@]
Include STLCFix\_subst\_Cases. [@\tanc{c-STLCFix-d-subst-start}@]
Def subst :=[@\hfill\codecomment{Instantiate \texttt{subst} \& its equalities}@]
  tm\__rect _ subst\_tm_unit subst\_tm_var
             subst\_tm_abs  subst\_tm_app subst\_tm_fix.
Fact[@\;@][@\textls[-40]{subst\_tm\_unit\_eq}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLCFix-d-subst-end}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{\textls[-10]{Instantiate \texttt{ty}, its constructors, partial recursor \& eq.}}@][@\tanc{c-STLCFix-d-ty}@][@\innersep@]
Include STLC\_env.[@\hfill\codecomment{Include \texttt{env}}@][@\tanc{c-STLCFix-d-env}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{Include/Instantiate other fields of family \texttt{STLCFix}}@][@\tanc{c-STLCFix-d-rest}@][@\innersep@]
[@\outdent@]End STLCFix.[@\tanc{c-STLCFix-end}@]
\end{lstlisting}

\makeline[.5\textwidth+8pt]{c-STLCFix-tm-start}{c-STLCFix-tm-end}[codecomment-color!50][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-subst-start}{c-STLCFix-subst-end}[codecomment-color!50][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-rest}{c-STLCFix-rest}[codecomment-color!50][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-start}{c-STLCFix-end}[codecomment-color!50][1.8pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-tm-start}{c-STLCFix-d-tm-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-subst-start}{c-STLCFix-d-subst-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-ty}{c-STLCFix-d-ty}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-env}{c-STLCFix-d-env}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-rest}{c-STLCFix-d-rest}[codecomment-color!35][1.0pt]
